Coherent optical association of a single molecule

### 2020-09-20 paper.tex
Update on Overleaf.

Diverse species of fully quantum controlled  ultracod molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and the studies of ultracold chemistry.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms. 
%(any place to cite  molecular ion work?)

Such ultracold molecular associating takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, an established two-step approach have been taken to first associate atom pairs into weakly-bound molecules, then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.  
So far, all of such association process  utilize a magnetic Feshbach scattering resonance. The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow excited states are available and optical association can be driven. The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap (and the narrow excited state) limits the   generality of the association technique to  more diverse species of molecules which are needed (or picked) for a desired application.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecules using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state. Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma$ that balances coupling/transfer efficiency and photon scattering. Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ... This approach is general and can be use to associate other molecular species or large molecules atom-by-atom.
%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

@@

(goes to SM?)

@@

>>>>

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules  below 1~mK~\cite{Norrgard2016}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the associations of ultracold atoms.
%(any place to cite  molecular ion work?)
% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.

Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms  as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach have been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from one internal state  to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, all of such association process  utilize a magnetic Feshbach scattering resonance and  apply to bialkali molecules. The only exception is Sr$_2$~\cite{Reinaudi2012,Stellmer2012} where narrow linewidth excited states are available and optical association can be driven. The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the narrow excited state lines limits the generality of the association technique to more diverse molecular species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using an optical Raman transfer via an electronic excited state, without the use of a Feshbach resonance nor a narrow excited state. Our scheme is based on theoretically determined most suitable vibrational state of the electronic excited state $c^3\Sigma^+$ that balances transfer coupling and photon scattering. Furthermore, to reduce technical requirements such as intensity stability, etc , we choose a initial and final state ... This approach is general and can be use to associate other molecular species or large molecules atom-by-atom.
%electronic the best initial hyperfine combination of the atoms to use and best single photon frequency that balances coupling/transfer efficiency and photon scattering. Using these parameters, we demonstrate coherent association of a electronic ground-state molecule from two atoms via an optical Raman transition in an optical tweezer.

@@

%(goes to SM?)

@@

In addition to the intermediate state, the choice of the initial and final states are critical for both fundamental and technical reasons. A key difference in molecular association via a Raman process compared to Raman transfer between hyperfine states in atoms is that the matrix elements between the ground states and the excited state are greatly unbalanced. In particular, the matrix element between the molecule state and the excited state, $ \Omega_m $ is much larger than the matrix element between the free atom state and the excited state, $ \Omega_a $. To understand the effect of this inbalance, we consider a 3 level model, and ignore the presence of multiple excited states. The Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$ depends on both matrix elements, but the scattering rate predominantly comes from the final molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth and $ \Delta $ is the single photon detuning. Assuming the power of each Raman beam is equal, there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning. Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. Thus, a small $ \Omega_m/\Omega_a $ ratio is desired to be able to drive this transition coherently. In addition to this fundamental reason, there is also a technical advantage for having a $ \Omega_m/\Omega_a $ ratio to be as small(? or big) as possible. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser needs to be stabilized to better than the inverse of this ratio, $ \Omega_a/\Omega_m $, to fluctuate by less than a linewidth. This becomes technically easier when $ \Omega_m/\Omega_a $ is smaller. 
(for our choice of states, this mean intensity fluctuation of less than 1\% or 0.1\%.)
